Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-09-07 draft.tex
simplify statement of prop 2 for decisive war
change statment of alpha and nu parameters to make them positive

Player $p$'s payoffs in period $n$ are $U_{pn}= \alpha X+\lambda Y -R_{pn}$, while the payoffs for player $c$ are $U_{cn}= \beta X+\nu Y -R_{cn}$, with both payoffs denoted in currency units.

The patron opposes reunification while player $c$ prefers it, so $\alpha$ is negative and $\beta$ is positive. The patron prefers recognized independence so $\lambda$ is positive. Player $c$ is averse to the creation of new states so $\nu$ is negative.

@@

\item \textit{The continuation value from playing Status Quo must fall below that from playing Cede before it falls below that from playing Fight. }
\end{enumerate}

>>>>

Player $p$'s payoffs in period $n$ are $U_{pn}= -\alpha X+\lambda Y -R_{pn}$, while the payoffs for player $c$ are $U_{cn}= \beta X-\nu Y -R_{cn}$, with both payoffs denoted in currency units. Taking $\alpha, \ \beta, \lambda,$ and $\nu$ to be positive, these payoffs represent the idea that the patron opposes reunification while player $c$ prefers it, and that the patron prefers recognized independence while player $c$ is averse to the creation of new states.

@@

\item \textit{The secessionists' continuation value from playing Cede must be higher than their continuation value from playing Fight. }
\end{enumerate}
